Numerical Stability of Detonations in White Dwarf Simulations

### 2018-07-12 papers/ignition/paper.tex
Move methodology section after introduction

\section{Numerical Instability}
\label{sec:instability}

% Discuss the Kushnir stability argument

%==========================================================================
% Problem Setup
%==========================================================================
\section{White Dwarf Collision Setup}
\label{sec:collisions}

%==========================================================================
% Numerical Implementation
%==========================================================================
\section{Numerical Methods}
\label{sec:numericalmethods}

The hydrodynamical equations solved in this paper were presented in \citet{wdmergerI}
(hereafter, Paper I) for the reacting hydrodynamics code \castro\ \citep{castro}.
Only minor revisions to the core hydrodynamic algorithm have since occurred.
In this paper we focus our discussion on our implementation of the nuclear
reaction network and integrator. There are three main areas of concern: first,
specifying what nuclides are in the network and what reaction rates link the
various nuclides; second, once the system of ODEs governing the evolution of
the nuclear species has been written down, how to couple them to ODEs governing
the evolution of the thermodynamics, in particular the temperature; third,
coupling the nuclear reaction updates to the evolution of the hydrodynamical
system. We will deal with each of these in turn in the following subsections.

\subsection{Nuclear Network}
\label{sec:network}

In this paper we use the \aproxthirteen\ network\ \citep{timmes:1999,timmes:2000}.
This includes all thirteen $\alpha$-chain particles between ${}^4$He and ${}^{56}$Ni.
These $\alpha$-chain particles capture the most important pathway connecting a WD
and its thermonuclear detonation. This network was used by \citet{hawley:2012}
and \citet{raskin:2010}. \citet{loren-aguilar:2010} and \citet{garcia-senz:2013} used a
very similar network that additionally included ${}^{60}$Zn. The \aproxthirteen\ network has been
ported into a form that is consistent with the \amrex\ codes in the freely available
\microphysics\ code repository\footnote{\microphysics\ can be obtained at
\url{https://github.com/starkiller-astro/Microphysics}.},
a collection of microphysical routines that are designed to be used in our
hydrodynamics codes. In our \microphysics\ repository we have also ported \aproxnineteen\
\citep{timmes:1999}, which was used in a few previous collision papers, and \aproxtwentyone.
The isotopes added by these networks relative to \aproxthirteen\ are not particularly relevant
to the problem of head-on white dwarf collisions, so we do not discuss results with these networks
here (though we have verified for this problem that these larger networks do not significantly change
the answer). We also make available \isoseven\ \citep{timmes:2000}, which skips the nuclides between
silicon and nickel, and which was used by \citet{rosswog:2009}. \isoseven\ gives significantly different
quantitative results than \aproxthirteen\ for this problem, due to its inapplicable assumption of
an equilibrium abundance of the unsimulated isotopes, but the results are still qualitatively similar.

@@

>>>>

\section{Nuclear Burning Methodology}
\label{sec:methodology}

In this section we discuss several issues in reactive hydrodynamic simulations and
how we addressed them in the \castro\ code \citep{castro}. We first describe the
core operation of our burner module, which is implemented in the \microphysics\ code
repository\footnote{\microphysics\ can be obtained at \url{https://github.com/starkiller-astro/Microphysics}.},
a collection of microphysical routines that are compatible with \castro.

@@

%==========================================================================
% 1D collision test problem
%==========================================================================
\section{Numerical Test Problem}
\label{sec:collisions}
